---
title: "DQR_dowJones_histFeatures_10y"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyr)
theme_set(theme_bw())
```



```{r}
data <- read.csv("../data/dowJones_histFeatures_10y.csv", stringsAsFactors = FALSE)
str(data)
```

# Data Structure

```{r}
table(data$year)
table(data$month)
table(data$variable)
summary(data$value)
```

# Distributions

```{r}
ggplot(data) +
  geom_histogram(aes(x = value), bins = 30) +
  facet_wrap(~variable, nrow = 2, scales = "free")
volas <- data$variable == "vola"
data$variable[volas] <- "logVola"
summary(data[volas, ]$value)
data$value[volas] <- log(data$value[volas])
ggplot(data) +
  geom_histogram(aes(x = value), bins = 30) +
  facet_wrap(~variable, nrow = 2, scales = "free")
```

# Correlation

```{r}
wide <- spread(data, variable, value)
ggplot(wide) +
  geom_point(aes(x = logVola, y = logReturn))
```

# Time Dependence

## Return

```{r}
wide$date <- as.Date(sprintf("%d-%d-1", wide$year, wide$month), format = "%Y-%m-%d")
ggplot(wide) +
  geom_path(aes(x = date, y = logReturn, group = isin, group = isin), alpha = .3)
```

## Volatility

```{r}
ggplot(wide) +
  geom_path(aes(x = date, y = logVola, group = isin, group = isin), alpha = .3)
```

# Subyearly Effects

## Return

```{r}
ggplot(wide) +
  geom_violin(aes(x = factor(month), y = logReturn), fill = "gray", color=NA) +
  geom_boxplot(aes(x = factor(month), y = logReturn), fill = NA)
```

## Volatility

```{r}
ggplot(wide) +
  geom_violin(aes(x = factor(month), y = logVola), fill = "gray", color=NA) +
  geom_boxplot(aes(x = factor(month), y = logVola), fill = NA)
```


# Filtering

Zunächst möchte ich erst mal auf Jahres basis arbeiten.
Deshalb sind nur Daten für ganze Jahre komplett.

```{r}
isReturn <- data$variable == "logReturn"
isVola <- data$variable == "logVola"
isins <- unique(data$isin)
```

For each ISIN, check whether there is volatility and return for each month
of a given year.

```{r}
getIsinsWithCompleteDataFor <- function(year) {
  isYear <- data$year == year
  isComplete <- sapply(isins, function(d) {
    isIsin <- data$isin == d
    if (sum(table(data[isIsin & isYear & isVola, ]$month)) < 12) {
      return(FALSE)
    } else if (sum(table(data[isIsin & isYear & isReturn, ]$month)) < 12) {
      return(FALSE)
    }
    return(TRUE)
  })
  return(isComplete)
}
```

Check that for each year

```{r}
fullYears <- data.frame(isin = isins)
for (year in sort(unique(data$year))) {
  fullYears[[as.character(year)]] <- getIsinsWithCompleteDataFor(year)
}
long <- gather(fullYears, year, complete, -isin)
```

```{r}
table(long$year, long$complete)
```
```{r}
fullYears$`2008` <- NULL
fullYears$`2018` <- NULL
long <- gather(fullYears, year, complete, -isin)
(incompleteIsins <- as.character(unique(long[!long$complete, ]$isin)))
```

* `US26078J1007` ist DowDuPoint
* `US02079K1079` ist Alphabet C
* `US30303M1027` ist Facebook

```{r}
for (isin in incompleteIsins) {
  print(isin)
  print(long[long$isin == isin & !long$complete, ]$year)
}
```

```{r}
table(data[data$isin == incompleteIsins[1], ]$year)
table(data[data$isin == incompleteIsins[2], ]$year)
table(data[data$isin == incompleteIsins[3], ]$year)
```

```{r}
data <- data[!data$isin %in% incompleteIsins, ]
data <- data[!data$year %in% c(2008, 2018), ]
```


# Final Set

```{r}
nrow(data)
length(unique(data$isin))
length(unique(data$year))
```

```{r}
write.csv(data, file = "../data/dowJones_histFeatures_10y_DQR_fullYears.csv",
          quote = FALSE, row.names = FALSE)
```


